### 2013-03-26 doc/sosp13/communication.tex
edits based on Jacob's feedback

\paragraph{Message aggregation} In our experiments the vast majority of upper
layer message requests are smaller than 44 bytes. Our measurements confirm
manufacturers' published data [15]; with 44-byte packets, the available
bisection bandwidth is only a small fraction (3\%) of the peak bisection
bandwidth. As mentioned earlier, commodity networks including InfiniBand
achieves their peak bisection bandwidth only when the packet sizes are
relatively large --- on the order of multiple kilobytes. The reason for this
discrepancy is the combination of overheads associated with handling each
packet (in terms of bytes that form the actual packet, processing time at the
card and processing on the CPU within the driver stack). Consequently, to make
the best use of the network, we must convert small messages into large ones.

@@

Once the remote system node has received the message buffer it is unpacked.
Upper level \Grappa messages are delivered to each core at the destination
system node by examining the message buffer at each processor core and then
handing the message buffer to the next core for delivery of messages destined
to that core.

>>>>

\paragraph{Message aggregation} In our experiments the vast majority of upper
layer message requests are smaller than 44 bytes. Our measurements confirm
manufacturers' published data [15]; with 44-byte packets, the available
bisection bandwidth is only a small fraction (3\%) of the peak bisection
bandwidth. As mentioned earlier, commodity networks including InfiniBand
achieves their peak bisection bandwidth only when the packet sizes are
relatively large --- on the order of multiple kilobytes. The reason for this
discrepancy is the combination of overheads associated with handling each
packet (in terms of bytes that form the actual packet, processing time at the
card, multiple roundtrips on the PCI express bus and processing on the CPU
within the driver stack). Consequently, to make the best use of the network,
we must convert small messages into large ones.

@@

Once the remote system node has received the message buffer, it is unpacked
and put int the corresponding incoming message lists. This process is done in
parallel by all system worker responsible for communication. Upper level
\Grappa messages are delivered to each core at the destination system node by
examining the message buffer at each processor core and then handing the
message buffer to the next core for delivery of messages destined to that
core.
